Nowadays, the development of the Internet brings about the revolution of blockchain, which is a technology that stores, verifies, transfers and communicates network data through its own distributed nodes without relying on a third party.

So blockchain can be regarded as a community of network, which contributes to the merchants’ cooperation. With its decentralization, it can help build an open system, which is called the loyalty points system. Any merchant can join in, so that the reward points and interests of different platforms can be flexibly transferred and more benefits will be created.

Compared with general \RPd\ system, the loyalty points systems based on blockchain have advantages in many aspects, the first of which is its characteristic of decentralization, which wins customers' trust. While \RPd\ in a general \RPd\ system can be easily tampered, the loyalty points system is open and transparent,so the technology of blockchain can serve as an easy solution to the trust crisis.

Besides, unlike general \RPd\ systems which give out \RPd\ freely, the loyalty points system has a fixed model. This means that a loyalty points system usually has a fixed total number of \RPd\ (or the total number of \RPd\ is linearly related to some variable), which brings about more commercial value.

As \RPd s in the loyalty points systems own its independent commercial value and are value-added, such \RPd\ can be approximately regarded as tokens. Compared with general \RPd\ which can only be exchanged, \RPd\ in the loyalty points systems can even be used as equity.

Loyalty point system today is gradually becoming the main type of \RPd\ systems. As a system with so many advantages, it will definitely bring more energy and vitality to the marketplace in the future.