\begin{enumerate}
	\itembf{Business size}
	
	As written in 4.2, only when the allies bear similar fame will the alliance be formed. And it can also apply to many-to-many alliances partly. For a many-to-many alliance, only big businesses can afford the cost of \RPd\ and benefit each other. (If only one merchant is famous enough, then most of its customers will go to other merchants in the alliance while itself will get a few new customers.) So a many-to-many alliance can only contain big businesses.
	
	\itembf{Product type}
	
	As the essential of the alliance does not change when the number of merchants rise, the impact of product type is similar.
	
	\begin{enumerate}
		\itembf{Difference}
		
		If the allies sell too similar products, they may get involved in vicious competitions, leading to unwanted results.
		
		\itembf{Correlation}
		
		Due to the mutual advertisements effect of the system, allies should maximize the stimulating effect of purchasing in its ally's store, so each ally's products should mostly fit in the potential shopping list of the one of others'.
	\end{enumerate}
	
	\itembf{Size of the community}
	
	Each merchant owns its own group of customers, adding up to their community. When a merchant joins in an alliance, its own community will be added to the alliance community. So the more merchants the alliance contains, the more its community will be, which means there will be more customers. (It should be remembered that different merchants may have same customers.)

\end{enumerate}
